\subsection{GDriveDownloader}
The GDriveDownloader class is responsible for authenticating to Google, acquiring a list of files from Google Drive, and downloading the file.
This class is able to take the authentication token and the built service as an input on creation.  
%​
\subsubsection{Associations}
\textbf{Main} 
The GDriveDownloader class is contained in `main', which will pass in authentication information and receive information about files 
that a user has access to.

\textbf{Google} 
The GDriveDownloader Class makes calls to Google.

\subsubsection{Attributes}

\textbf{GDriveDownloader\_creds} \\
The attribute GDriveDownloader\_creds holds the authentication token.

\textbf{GDriveDownloader\_SCOPES} \\
The attribute GDriveDownloader\_SCOPES holds the scope of what the application can access from Google.

\textbf{GDriveDownloader\_service} \\
The attribute GDriveDownloader\_service holds the built service.

\textbf{GDriveDownloader\_file\_List} \\
The attribute GDriveDownloader\_file\_List holds the list of files from Google Drive.

\textbf{GDriveDownloader\_json} \\
The attribute GDriveDownloader\_json holds the JSON needed by the UI.

\textbf{GDriveDownloader\_files\_to\_download} \\
The attribute GDriveDownloader\_files\_to\_download holds a list of dictionaries.

\subsubsection{Methods}
\textbf{GDriveDownloader\_authentication} \\
This method handles the authentication to Google and gets the authentication token. It saves the token in GDriveDownloader\_creds.

\textbf{GDriveDownloader\_save\_Token} \\
This method saves the token to a file.

\textbf{GDriveDownloader\_load\_Token} \\
This method loads the token from a file.

\textbf{GDriveDownloader\_build\_Service} \\
This method builds the service from the scope and the authentication token.

\textbf{GDriveDownloader\_\_download\_File} \\
This method loops overGDriveDownloader\_files\_to\_download and downloads the files to the working dictionary. 

\textbf{GDriveDownloader\_\_get\_Files} \\
This method queries Google Drive for the files stored in the user's Google account. It will also create the JSON for the UI and store it in GDriveDownloader\_json.   

\textbf{GDriveDownloader\_add\_file\_to\_download} \\
This method takes a dictionary with keys 'name' and 'id' as input and appends it to overGDriveDownloader\_files\_to\_download.

\textbf{GDriveDownloaded\_authentication\_flow} \\
This method creates the autentication flow using the seceret from google.

\textbf{GDriveDownloaded\_authentication\_start} \\
This method get the url to redirect to google's login page.

\textbf{GDriveDownloaded\_authentication\_finish} \\
This method gets a json with the access token, turns it into a Credential object, builds the service and gets the files. It then redircts to the files page. 
